Beliefs about the development of mental life

### 2024-12-31 paper/paper.Rmd
typos and rerun from scratch

Indeed, caring for a young child involves making countless decisions under uncertainty: Why is my child crying, smiling, shouting, or biting? What do they want, and what do they need? Can they understand what I am saying? Do they love me? As in other domains of reasoning[@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children's behavior and development, with consequences for the well-being of children in their care.

@@

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce). All studies were approved by the Institution Review Board for Human Subjects at Stanford University. For extended descriptions of methods and results, see Supplemental Materials.

@@

The second factor corresponded primarily to what we would describe as social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we that we interpreted as reflecting a higher-order capacity for _social connection_. It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "getting pleasure from music," "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others, recognizing others, fearing others, listening to others), and because we interpret this factor as indexing participants' sense of the infant awakening into the human social and cultural world. This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants' capacity attributions.

>>>>

Indeed, caring for a young child involves making countless decisions under uncertainty: Why is my child crying, smiling, shouting, or biting? What do they want, and what do they need? Can they understand what I am saying? Do they love me? As in other domains of reasoning [@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children's behavior and development, with consequences for the well-being of children in their care.

@@

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce). All studies were approved by the Research Compliance Office, Human Subjects Panel (IRB) at Stanford University. For extended descriptions of methods and results, see Supplemental Materials.

@@

The second factor corresponded primarily to what we would describe as social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we that we interpreted as reflecting a higher-order capacity for _social connection_. It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others, recognizing others, fearing others, listening to others), and because we interpret this factor as indexing participants' sense of the infant awakening into the human social and cultural world. This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants' capacity attributions.
